%!TEX root = ../pres.tex

\begin{frame}
	\center\huge{Practical Reinforcement Learning}
\end{frame}

\begin{frame}
\frametitle{Process}
\begin{enumerate}
	\item Clearly define the environment.
	\begin{itemize}
		\item What is state space, $\scripts$? Action space $\scripta?$ Low dimensions is better!
		\item Use tools like OpenAI Gym to make a simulator.
	\end{itemize}
	\item Choose a good reward function.
	\begin{itemize}
		\item Don't make sparse reward functions: \\
		\begin{center}
			\textbf{+1 for winning vs. guiding agent to win.}
		\end{center}
		\item Penalize for time constraints!
		\item Break the problem in to smaller goals with rewards $r_1, r_2,\dots$. Then
			$r(s,a) = \sum_i w_i r_i(s,a)$.
	\end{itemize}
\end{enumerate}
\end{frame}


\begin{frame}
\frametitle{Process}
\begin{enumerate}

	\setcounter{enumi}{2}
	\item Choose a model.
	\begin{itemize}
		\item Deep reinforcement learning is king! 
		\begin{itemize}
			\item Discrete $\scripta \to DQN, DDQN$
			\item Continuous $\scripta \to DDPG, NAF, A3C, TRPO.$	
		\end{itemize}
		\item Less hyperparameters better.
		\item Don't rule models out too early.
	\end{itemize}
	\item Train the model against the environment.
	\begin{itemize}
		\item Choose a good exploration strategy.
		\item RL can take a long time (days - months), let models train to completion.
		\item Do a sweep on hyperparameters.
		\item Overfitting (to optimal policy) is good. 
		\item \emph{(You will fail here many times, go to step 3.)}
	\end{itemize}
	\item Profit
\end{enumerate}
\end{frame}



\begin{frame}
\frametitle{$\text{ProTips}^{tm}$}
\begin{itemize}
	\item \textbf{Fastest way to learn RL:} Implement landmark papers in tensorflow, Atari DQN, DPG, ...
	\item \textbf{Write unit tests before you train!}
	\item \textbf{Use an autodiff framework: } Tensorflow, PyTorch, ...
	\item \textbf{Avoid pixel data at all costs: } CNNs/CV algorithms make training very slow!
	\begin{itemize}
		\item Test RL models on featurized data in simualtion, then move to pixel based models for real data.
	\end{itemize}
\end{itemize}
\begin{center}
	\textbf{Good luck!}
\end{center}
\end{frame}
